Supplementary Information

### 2015-06-28 manuscript/supplement.tex
Updated pred-prey lists and code for new updated web

  We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011}, 
  and~\citet{Dunne2013}.
  Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
  source was unpublished or could not be retrieved. We further eliminated 13 source or sink webs
  (which describe feeding links flowing from or to a particular resource or top predator rather
  than the interactions of an entire community), 8 plant-pollinator webs, 34 host-parasitoid webs,
  and 2 networks describing competitive interactions. Finally, we eliminated 2 webs describing 
  inferred interactions in an extinct community, 8 ``generalized schemes'' that were not based
  on direct field data, and 2 webs where it was not clear which of several described study sites
  were used to construct the food web (and therefore the latitude of the food web could not be 
  included). This left us with 156 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
  free-living species, we removed the the parasites (and all interactions involving them) from
  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
  species only. In addition, we included 30 of the 35 webs from~\citet{Riede2011}, which were originally
  collected to test the relationship between consumer and
  resources body sizes. The remaining webs the~\citet{Brose2005}
  dataset were also included in the~\citet{GlobalWeb} 
  dataset. This gave us a database of 264 webs. As we
  wished to use the logarithmic form of power-law
  relationships, we then eliminated any food web which
  did not have at least one each of basal resources,
  intermediate consumers, and top predators (to obtain 
  non-zero proportions of each category). Our final sample
  size was thereby reduced to 197 food webs.

>>>>

  We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011},
  and~\citet{Dunne2013}. Of the 358 food webs available
  from~\citet{Globalweb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalized
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\citet{GlobalWeb} contained only free-living species, we removed the
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\citet{Riede2011}, which were originally collected to test the
  relationship between consumer and resources body sizes. Nine of the
  remaining webs in the~\citet{Riede2011} dataset were also included in
  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. As we wished to use
  the logarithmic form of power-law relationships, we then eliminated any food
  web which did not have at least one each of basal resources, intermediate
  consumers, and top predators (to obtain  non-zero proportions of each
  category). Our final sample size was thereby reduced to XXX food webs.
